### 2021-07-02 doc/thesis/chapters/introduction.tex
introduction done for now

\section{Goal}

@@

develop an FM receiver and explain it, so that it can be followed in a tutorial with an affordable budget in hardware.\\
show multiple ways of how to implement the same thing, in different levels of abstraction. Weigh each ways' field of application, efficiency and applicability.

%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%

Thesis Design Decisions: \\
\\
Main focus on system design. \\
\\
How to achieve the same result in 3 (4?) different levels of abstraction?

\begin{enumerate}
  \item GnuRadio (?)
  \item Matlab/Python
  \item HLS\\
      Implementation targeting Xilinx' ZedBoard.\\
      Optionally: \\
      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
  \item VHDL
\end{enumerate}
\vspace{.5 cm}

Compare:
- Implementation effort (difficulty)
- Implementation time
- Usefulness on Target Systems (uC, SoC, RasPi, etc)
- others?

>>>>

\section{Goals}

@@

In the view of a system design approach, another focus is put on a sustainable testing and development strategy for the entire system.
Above mentioned implementation variants should optimally share as much as possible of verification code, in order to save time and effort in implementation.
Also, as many tasks as possible should be automated by scripts, to save time in manual labor for the software engineers.
All that enables an efficient development cycle of the product.

By the end of this thesis, the implementation of an FM radio receiver in multiple methods and abstraction levels should be achieved, as well as a good understanding of the overall system level design.
Knowledge of each methods' preferred field of application, efficiency and application should be gained.

%develop an FM receiver and explain it, so that it can be followed in a tutorial with an affordable budget in hardware.\\

%%%%%%%%%%%%%%%%%%%%%%%
% NOTES:
%%%%%%%%%%%%%%%%%%%%%%%
%
%Thesis Design Decisions: \\
%\\
%Main focus on system design. \\
%\\
%How to achieve the same result in 3 (4?) different levels of abstraction?
%
%\begin{enumerate}
%  \item GnuRadio (?)
%  \item Matlab/Python
%  \item HLS\\
%      Implementation targeting Xilinx' ZedBoard.\\
%      Optionally: \\
%      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
%  \item VHDL
%\end{enumerate}
%\vspace{.5 cm}
%
%Compare:
%- Implementation effort (difficulty)
%- Implementation time
%- Usefulness on Target Systems (uC, SoC, RasPi, etc)
%- others?
